\vspace{-2cm}A generative model for urban firm networks

### 2022-05-23 main.tex
Update on Overleaf.

\\
Juste Raimbault\textsuperscript{1,2,3,4 *},
Natalia Zdanowska\textsuperscript{2,4,5},
Elsa Arcaute\textsuperscript{2}
\\
\bigskip
\textbf{1} LASTIG, Univ Gustave Eiffel, IGN-ENSG, Saint-Mand{\'e}, France
\\
\textbf{2} Centre for Advanced Spatial Analysis, UCL, London, United Kingdom
\\
\textbf{3} UPS CNRS 3611 ISC-PIF, Paris, France
\\
\textbf{4} UMR CNRS 8504 G{\'e}ographie-cit{\'e}s, Paris, France
\\
\textbf{5} Luxembourg Institute of Socio-Economic Research, Esch-sur-Alzette, Luxembourg

@@

These two indicators capture the overall model performance with the logarithm of MSE, but also performance on medium-sized and small links, and are therefore complementary as shown in the case of cities population dynamics by \cite{raimbault2018indirect}. A calibration on macroscopic indicators of metropolisation and internationalisation would not bring much knowledge on model processes, since several points from the grid experiment above - not designed for this - already provide a good performance (19 parameter points out of 6534 are simultaneously below a relative error of 10\% on internationalisation and below 10\% on metropolisation).

>>>>

Juste Raimbault\textsuperscript{1,2,3,4 *},
Natalia Zdanowska\textsuperscript{2,4,5},
Elsa Arcaute\textsuperscript{2}
\\
\bigskip
\textbf{1} LASTIG, Univ Gustave Eiffel, IGN-ENSG, Saint-Mand{\'e}, France
\\
\textbf{2} Centre for Advanced Spatial Analysis, UCL, London, United Kingdom
\\
\textbf{3} UPS CNRS 3611 ISC-PIF, Paris, France
\\
\textbf{4} UMR CNRS 8504 G{\'e}ographie-cit{\'e}s, Paris, France
\\
\textbf{5} Luxembourg Institute of Socio-Economic Research, Esch-sur-Alzette, Luxembourg

@@

These two indicators capture the overall model performance with the logarithm of MSE, but also performance on medium-sized and small links, and are therefore complementary as shown in the case of cities population dynamics by \cite{raimbault2018indirect}. A calibration on macroscopic indicators of metropolisation and internationalisation would not bring much knowledge on model processes, since several points from the grid experiment above - not designed for this - already provide a good performance: 19 parameter points out of 6534 are simultaneously below a relative error of 10\% on internationalisation and below 10\% on metropolisation. These points correspond to diverse parametrisation, suggesting the presence of equifinality when trying to calibrate at the macroscopic level.
